### 2019-04-02 thesis_supports/Response_Reviewer1/Response_Reviewer1.tex

\documentclass[dvips,a4paper,12pt]{report}
\usepackage{xcolor}
\usepackage[
    top=0.6in,
    bottom=0.6in,
    right=0.6in,
    left=0.6in]{geometry}

\begin{document}
\pagenumbering{arabic}

% ----------------------------------------- Begin content --------------------------------------------- %
%%% letter
\noindent Respected Examiner,

\noindent Thank you for reviewing my thesis.

\begin{center}
    \textbf{Thesis Title: Implementation of an Autonomous Star Recognition Algorithm using Hardware-Software Co-processing Approach} 
\end{center}

\noindent Firstly, I would like to thank you for your insightful comments. These excellent comments have helped significantly improve my thesis. This letter addresses each of the raised points and notes precisely how I have responded and included the comments into my revised thesis. \\

\vspace{0.5in}

\noindent Sincerely yours,

\noindent Dang Le Dang Khoa

%%% Q&A
\newpage

\color{blue}
\noindent \large{\textbf{Examiner: 1}}

\begin{enumerate}
    \color{blue}
    \item There are some obvious typos and format problems in the thesis. For example, in Page 7, the caption ‘table 2.1’ is written, but the whole table is given in Page 8. Please check and correct them.

    \color{black}
    Answer

    \color{blue}
    \item In this thesis, the author shows some figures such as Fig. 2.2, 2.3 without any explanation. Please add some explanation to these figures in the thesis content.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 3.3.1, the author applied thresholding technique in order to eliminate the noise and separate star clusters from the background. But the author did not explain how to choose the threshold.

    \color{black}
    Answer

    \color{blue}
    \item The author claimed that the proposed prebuilt tree structured star pattern database (SPD) was able to reduce space complexity while maintaining high accuracy and robustness, so this optimized algorithm could be used for nanosatellites which have limited memory. However, there is no comparison between the SPD algorithm and traditional algorithm on accuracy, storage consumption, and robustness in this thesis.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 4.2, the author compares runtime spent by traditional methods and the proposed method in this thesis. He lists specific software runtime and hardware – software co-processing runtime when the same image dataset is used. Details of images used in experiments are also provided. However, the author only lists tables and figures to show image specifications and runtime. He does not give even one word to explain or conclude his experiment results.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 4.1, the author gives experiment results showing hardware consumption and power consumption when the proposed method is applied. But he does not give comparison on consumption between traditional methods and his own method, therefore, readers do not know how to evaluate his experiment results. If he could add experiment results about power and hardware consumption when traditional methods are used (under the same experimental conditions), and then give a comparison between traditional methods and his method, the advantages of his proposed method would be clearer.

    \color{black}
    Answer

\end{enumerate}

% ----------------------------------------- End content --------------------------------------------- %
\end{document}

### 2019-04-02 thesis_supports/Response_Reviewer2/Response_Reviewer2.tex

\noindent Sincerely yours,

\noindent Dang Le Dang Khoa

%%% Q&A
\newpage

\color{blue}
\noindent \large{\textbf{Examiner: 2}}

\begin{enumerate}
    \color{blue}
    \item There are many careless mistakes in the thesis. Tables and figures are not explained in the body of the thesis, equations are given without explanations, unfinished sentences, etc. All these are indicated on the relevant pages in the thesis. Please correct and give explanations as requested.

@@

    \color{black}
    Answer

    \color{blue}
    \item Page 29. Please explain why the threshold is chosen to be 70 to separate star clusters from the background. That will happen if the threshold is reduced or increase?

@@

    \color{black}
    Answer

    \color{blue}
    \item Conclusion must be made for the study, so I would like to see a chapter on conclusion which includes the following:
    \begin{enumerate}[label=(\alph*)]
        \color{blue}
        \item One of the objective of the candidate's thesis is to implement and evaluate the performance of a star tracking algorithm, so what is the conclusion of the evaluation of the performance? Can it be used for the attitude determination sensor mounted on a spacecraft?

@@

        \color{black}
        Answer

        \color{blue}
        \item Another objecttive of the thesis is to benchmark and optimize the algorithm in terms of the poer consumption and the area of transistor implementation. What is the conclusion? What is the benchmark now? Did the candidate do optimization? What I got from the thesis are just the results of the power consumed, but it is necessary that the candidate describes how he did the optimization.

        \color{black}
        Answer
    \end{enumerate}

### 2019-04-03 thesis_supports/Response_Reviewer2/Response_Reviewer2.tex

\documentclass[dvips,a4paper,12pt]{report}
\usepackage{xcolor}
\usepackage{float}
\usepackage{enumitem}
\usepackage{graphicx}
    \graphicspath{ {./img/} }
\usepackage[
    top=0.6in,
    bottom=0.6in,
    right=0.6in,
    left=0.6in]{geometry}

@@

%%% Q&A
\newpage

\color{blue}
\noindent \large{\textbf{Examiner: 2}}

\begin{enumerate}
    \color{blue}
    \item There are many careless mistakes in the thesis. Tables and figures are not explained in the body of the thesis, equations are given without explanations, unfinished sentences, etc. All these are indicated on the relevant pages in the thesis. Please correct and give explanations as requested.

    \color{black}
    Thanks for pointing these out in your ``Additional Document'' file. I have checked and fixed them all. I also have amended detailed explanations and restructured Chapter 3 and 4. \\

    \color{blue}
    \item Page 29. Please explain why the threshold is chosen to be 70 to separate star clusters from the background. What will happen if the threshold is reduced or increase?

    \color{black}
    I have amended a precise explanation to chapter 3.3.1 Centroiding (pages: 28,29,30). To summarize how to choose the threshold value:

    \begin{itemize}
        \item Firstly, I perform an analysis by averaging and counting the occurences of all pixel values in the star image dataset. 
        \item The result of the analysis would form a pattern which is shown like the below image. It includes 2 significant clusters: the first cluster is the background pixel values which formed near 0 Intensity value and the second cluster is the star pixel value which formed near the 255 Intensity value and scattered data points in between(which represent the noise)
        \item Based on the analysis, We know the range of threshold value is in between the noise values and the star pixel cluster.
        \item Finally, while carrying out experiments on the test dataset, we fine-tune and optimize the threshold value to produce the highest possible accuracy.
    \end{itemize}

    \begin{figure}[H]
        \centering
        \includegraphics[width=1.0\textwidth]{4}
    \end{figure}

    If we set the threshold too low, it would lead to mismatches. Otherwise, if we set the threshold too high, some stars would be missing from the image.

    \color{blue}
    \item Conclusion must be made for the study, so I would like to see a chapter on conclusion which includes the following:

    \begin{enumerate}[label=(\alph*)]
        \color{blue}
        \item One of the objective of the candidate's thesis is to implement and evaluate the performance of a star tracking algorithm, so what is the conclusion of the evaluation of the performance? Can it be used for the attitude determination sensor mounted on a spacecraft?

        \color{black}
        I have amended some details to the summary and future works in Chapter 5. For the question ``Can it be used for the attitude determination sensor mounted on a spacecraft?'', based on the final Runtime Comparison results, the answer is yes since the runtime meet the requirements. In the future works section, I suggested a depth study on noise to implement a hardware module that performs the noise cancellation efficiently since my implementation only deals with basic noise. Furthermore, we need an autonomous input-processing module that can manage a large stream amount of images to meet the processing rate and improve the throughput. (This task would be depended on each specific spacecraft). \\

        \color{blue}
        \item Another objective of the thesis is to benchmark and optimize the algorithm in terms of the power consumption and the area of transistor implementation. What is the conclusion? What is the benchmark now? Did the candidate do optimization? What I got from the thesis are just the results of the power consumed, but it is necessary that the candidate describes how he did the optimization.

        \color{black}
        I have amended some details to Chapter Hardware design(restructured to Chapter 4.2 from page 45 to page 48). I have added a conclusion that the hardware-software co-processing approach is advantageous than the software-only approach in term of power consumption.

        The hardware design is written on a high-level language and relied on specific Xilinx design rules and optimizations like Loop pipelining to enhance the processing speed. My optimization was mostly done in the algorithmic level like transfer dependant loops to independent loops, transfer array index to a stream and indexing by the binary search to reduce BRAM storages. Since they are technical and specific, I would not prefer to include in the thesis. An optimization has been mentioned in the thesis is using the one-pass scan algorithm to solve the connected component problem without using complicated data structures to reduce the hardware runtime. \\

### 2019-04-03 thesis/2_chapters/chap3.tex
Pre Final check

% Figure 3.2
\ntuepsfig[width=\textwidth]{3_2}{An ARM embedded processor}

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background. \\

\noindent Most of the star images are affected by noise. Sometimes, the star tracker misleads the noise as a star which often leads to a mismatch. Therefore, the threshold should be carefully chosen. If we set the threshold too low, it would lead to mismatches. Otherwise, if we set the threshold too high, some stars would be missing from the image. Between 0-255, we choose the threshold value 70 which mostly produce high matching accuracy.

@@

@@

The raw image is contaminated with noises and other non-stellar objects. These noises can be canceled by setting a threshold level. If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern. After all false star noise is canceled, the centroiding algorithm proceeds. \\

>>>>

% Figure 3.2
% \ntuepsfig[width=\textwidth]{3_2}{An ARM embedded processor}

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by the Average Pixel Intensity technique. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background. \\

\noindent Most of the star images are affected by noise. Sometimes, the star tracker misleads the noise as a star which often leads to a mismatch. Therefore, the threshold should be carefully chosen. If we set the threshold too low, it would lead to mismatches. Otherwise, if we set the threshold too high, some stars would be missing from the image.

@@

\noindent The Average Pixel Intensity technique is applied to choose the threshold value. Firstly, we perform an analysis by averaging and counting the occurrences of all the pixel values in the star image dataset. The pattern of the analysis is simulated as in Figure~\ref{fig:3_24}. It includes 2 significant clusters: the first cluster is the background pixel values which formed near 0 Intensity value and the second cluster is the star pixel value which formed near the 255 Intensity value. There will be some scattered data points in between which represent the noise values. Based on the pattern we may know the range of the threshold value. To select the threshold value precisely, while running the algorithm on the test dataset, we fine-tune the threshold value again within the range to achieve the best accuracy. After performing the analysis and carrying out the algorithm on the test dataset, we choose the threshold value 70 which mostly produce high matching accuracy. \\

\ntuepsfig[width=\textwidth]{3_24}{Clustering pixel values}

@@

The raw image is contaminated with noises and other non-stellar objects. The noise can be canceled by setting a threshold level. If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern. After all false star noise is canceled, the centroiding algorithm proceeds. \\
